\chapter{The Bard}


 The poems say an adventurer's life is all open roads and the glory of coin and combat. The tales told in every farmhand-filled inn have to have some ring of truth to them, don't they? The songs to inspire peasantry and royals alike--to soothe the savage beast or drive men to a frenzy--have to come from somewhere.


 Enter the bard. You, with your smooth tongue and quick wit. You teller-of-tales and singer-of-songs. It takes a mere minstrel to retell a thing but a true bard to live it. Strap on your boots, noble orator. Sharpen that hidden dagger and take up the call. Someone's got to be there, fighting shoulder-to-shoulder with the goons and the thugs and the soon-to-be-heroes. Who better than you to write the tale of your own heroism?


 Nobody. Get going.
\section{Names}


 \emph{Elf}
: Astrafel, Daelwyn, Feliana, Damarra, Sistranalle, Pendrell, Melliandre, Dagoliir


 \emph{Human}
: Baldric, Leena, Dunwick, Willem, Edwyn, Florian, Seraphine, Quorra, Charlotte, Lily, Ramonde, Cassandra
\section{Look}


 Choose one for each:

\begin{itemize}
\item Knowing Eyes, Fiery Eyes, or Joyous Eyes


\item Fancy Hair, Wild Hair, or Stylish Cap


\item Finery, Traveling Clothes, or Poor Clothes


\item Fit Body, Well-fed Body, or Thin Body
\end{itemize}
\section{Stats}


 Your maximum HP is 6+Constitution.


 Your base damage is d6.
\section{Starting Moves}


 Choose a race and gain the corresponding move:
\subsection{Elf}


 When you enter an important location (your call) you can ask the GM for one fact from the history of that location.
\subsection{Human}


 When you first enter a civilized settlement someone who respects the custom of hospitality to minstrels will take you in as their guest.


 You start with these moves:
\subsection{Arcane Art}


 When you\textbf{weave a performance into a basic spell}
, choose an ally and an effect:
\begin{itemize}
\item Heal 1d8 damage
\item +1d4 forward to damage
\item Their mind is shaken clear of one enchantment
\item The next time someone successfully assists the target with aid, they get +2 instead of +1

\end{itemize}


 Then roll+Cha. *On a 10+, the ally gets the selected effect. *On a 7-9, your spell still works, but you draw unwanted attention or your magic reverberates to other targets affecting them as well, GM's choice.
\subsection{Bardic Lore}


 Choose an area of expertise:
\begin{itemize}
\item Spells and Magicks
\item The Dead and Undead
\item Grand Histories of the Known World
\item A Bestiary of Creatures Unusual
\item The Planar Spheres
\item Legends of Heroes Past
\item Gods and Their Servants

\end{itemize}


 When you \textbf{first encounter an important creature, location, or item (your call) covered by your bardic lore}
 you can ask the GM any one question about it; the GM will answer truthfully. The GM may then ask you what tale, song, or legend you heard that information in.
\subsection{Charming and Open}


 When you \textbf{speak frankly with someone}
, you can ask their player a question from the list below. They must answer it truthfully, then they may ask you a question from the list (which you must answer truthfully).
\begin{itemize}
\item Whom do you serve?
\item What do you wish I would do?
\item How can I get you to \_\_\_\_\_\_?
\item What are you really feeling right now?
\item What do you most desire?

\end{itemize}
\subsection{A Port in the Storm}


 When you \textbf{return to a civilized settlement you've visited before}
, tell the GM when you were last here. They'll tell you how it's changed since then.
\section{Alignment}


 Choose an alignment:
\subsection{Good}


 Perform your art to aid someone else.
\subsection{Neutral}


 Avoid a conflict or defuse a tense situation.
\subsection{Chaotic}


 Spur others to significant and unplanned decisive action.
\section{Gear}


 Your load is 9+Str. You have dungeon rations (5 uses, 1 weight). Choose one instrument, all are 0 weight for you:
\begin{itemize}
\item Your father's mandolin, repaired
\item A fine lute, a gift from a noble
\item The pipes with which you courted your first love
\item A stolen horn
\item A fiddle, never before played
\item A songbook in a forgotten tongue

\end{itemize}


 Choose your clothing:
\begin{itemize}
\item Leather armor (1 armor, 1 weight)
\item Ostentatious clothes (0 weight)

\end{itemize}


 Choose your armament:
\begin{itemize}
\item Dueling rapier (close, precise, 2 weight)
\item Worn bow (near, 2 weight), bundle of arrows (3 ammo, 1 weight), and short sword (close, 1 weight)

\end{itemize}


 Choose one:
\begin{itemize}
\item Adventuring gear (1 weight)
\item Bandages (0 weight)
\item Halfling pipeleaf (0 weight)
\item 3 coins

\end{itemize}
\section{Bonds}


 Fill in the name of one of your companions in at least one:


 This is not my first adventure with \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_.


 I sang stories of \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ long before I ever met them in person.


 \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ is often the butt of my jokes.


 I am writing a ballad about the adventures of \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_.


 \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ trusted me with a secret.


 \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ does not trust me, and for good reason.
\section{Advanced Moves}


 {\Large When you gain a level from 2-5, choose from these moves.}
\subsection{Healing Song}


 When you \textbf{heal with arcane art}
, you heal +1d8 damage.
\subsection{Vicious Cacophony}


 When you \textbf{grant bonus damage with arcane art}
, you grant an extra +1d4 damage.
\subsection{It Goes To Eleven}


 When you \textbf{unleash a crazed performance}
 (a righteous lute solo or mighty brass blast, maybe) choose a target who can hear you and roll+Cha. *On a 10+ the target attacks their nearest ally in range. *On a 7--9 they attack their nearest ally, but you also draw their attention and ire.
\subsection{Metal Hurlant}


 When you \textbf{shout with great force or play a shattering note}
 choose a target and roll+Con. *On a 10+ the target takes 1d10 damage and is deafened for a few minutes. *On a 7--9 you still damage your target, but it's out of control: the GM will choose an additional target nearby.
\subsection{A Little Help From My Friends}


 When you \textbf{successfully aid someone}
 you take +1 forward as well.
\subsection{Eldritch Tones}


 Your arcane art is strong, allowing you to choose two effects instead of one.
\subsection{Duelist's Parry}


 When you hack and slash, you take +1 armor forward.
\subsection{Bamboozle}


 When you \textbf{parley with someone}
, on a 7+ you also take +1 forward with them.
\subsection{Multiclass Dabbler}


 Get one move from another class. Treat your level as one lower for choosing the move.
\subsection{Multiclass Initiate}


 Get one move from another class. Treat your level as one lower for choosing the move.

\vspace{\baselineskip}
 {\Large When you gain a level from 6-10, choose from these moves or the level 2-5 moves.}
\subsection{Healing Chorus}


 Replaces: Healing Song


 When you \textbf{heal with arcane art}
, you heal +2d8 damage.
\subsection{Vicious Blast}


 Replaces: Vicious Cacophony


 When you \textbf{grant bonus damage with arcane art}
, you grant an extra +2d4 damage.
\subsection{Unforgettable Face}


 When you \textbf{meet someone you've met before}
 (your call) after some time apart you take +1 forward against them.
\subsection{Reputation}


 When you \textbf{first meet someone who's heard songs about you}
, roll+Cha. *On a 10+, tell the GM two things they've heard about you. *On a 7-9, tell the GM one thing they've heard, and the GM tells you one thing.
\subsection{Eldritch Chord}


 Replaces: Eldritch Tones


 When you use arcane art, you choose two effects. You also get to choose one of those effects to double.
\subsection{An Ear For Magic}


 When you \textbf{hear an enemy cast a spell}
 the GM will tell you the name of the spell and its effects. Take +1 forward when acting on the answers.
\subsection{Devious}


 When you use charming and open you may also ask ``How are you vulnerable to me?'' Your subject may not ask this question of you.
\subsection{Duelist's Block}


 Replaces: Duelist's Parry


 When you hack and slash, you take +2 armor forward.
\subsection{Con}


 Replaces: Bamboozle


 When you \textbf{parley with someone}
, on a 7+ you also take +1 forward with them and get to ask their player one question which they must answer truthfully.
\subsection{Multiclass Master}


 Get one move from another class. Treat your level as one lower for choosing the move.


