\chapter{The Ranger}


 These city-born folk you travel with. Have they heard the call of the wolf? Felt the winds howl in the bleak deserts of the East? Have they hunted their prey with the bow and the knife like you? Hell no. That's why they need you.


 Guide. Hunter. Creature of the wilds. You are these things and more. Your time in the wilderness may have been solitary until now, but the call of some greater thing--call it fate if you like--has cast your lot with these folk. Brave, they may be. Powerful and strong, too. You know the secrets of the spaces between, though.


 Without you, they'd be lost. Blaze a trail through the blood and dark, strider.
\section*{Names}


 \emph{Elf}
: Throndir, Elrosine, Aranwe, Celion, Dambrath, Lanethe


 \emph{Human}
: Jonah, Halek, Brandon, Emory, Shrike, Nora, Diana
\section*{Look}


 Choose one for each:

\begin{itemize}
\item Wild Eyes, Sharp Eyes, or Animal Eyes


\item Hooded Head, Wild Hair, or Bald


\item Cape, Camouflage, or Traveling Clothes


\item Lithe Body, Wild Body, or Sharp Body
\end{itemize}
\section*{Stats}


 Your maximum HP is 8+Constitution.


 Your base damage is d8.
\section*{Starting Moves}


{\bfseries Choose a race and gain the corresponding move:}
\subsection{Elf}


 When you undertake a perilous journey through wilderness whatever job you take you succeed as if you rolled a 10+.
\subsection{Human}


 When you make camp in a dungeon or city, you don't need to consume a ration.


\vspace{\baselineskip}
{\bfseries You start with these moves:}
\subsection{Hunt and Track (Wis)}


 When you \textbf{follow a trail of clues left behind by passing creatures}
, roll+WIS. *On a 7+, you follow the creature's trail until there's a significant change in its direction or mode of travel. *On a 10+, you also choose 1:
\begin{itemize}
\item Gain a useful bit of information about your quarry, the GM will tell you what
\item Determine what caused the trail to end

\end{itemize}
\subsection{Called Shot}


 When you \textbf{attack a defenseless or surprised enemy at range}
, you can choose to deal your damage or name your target and roll+DEX.
\begin{itemize}
\item Head *10+: As 7--9, plus your damage *7-9: They do nothing but stand and drool for a few moments.
\item Arms *10+: As 7-9, plus your damage *7-9: They drop anything they're holding.
\item Legs *10+: As 7-9, plus your damage *7-9: They're hobbled and slow moving.

\end{itemize}
\subsection{Animal Companion}


 You have a supernatural connection with a loyal animal. You can't talk to it per se but it always acts as you wish it to. Name your animal companion and choose a species:


 Wolf, cougar, bear, eagle, dog, hawk, cat, owl, pigeon, rat, mule


 Choose a base:
\begin{itemize}
\item Ferocity +2, Cunning +1, 1 Armor, Instinct +1
\item Ferocity +2, Cunning +2, 0 Armor, Instinct +1
\item Ferocity +1, Cunning +2, 1 Armor, Instinct +1
\item Ferocity +3, Cunning +1, 1 Armor, Instinct +2

\end{itemize}


 Choose as many strengths as its ferocity:


 Fast, burly, huge, calm, adaptable, quick reflexes, tireless, camouflage, ferocious, intimidating, keen senses, stealthy


 Your animal companion is trained to fight humanoids. Choose as many additional trainings as its cunning:


 Hunt, search, scout, guard, fight monsters, perform, labor, travel


 Choose as many weaknesses as its instinct:


 Flighty, savage, slow, broken, frightening, forgetful, stubborn, lame
\subsection{Command}


 When you work with your animal companion on something it's trained in \ldots 
\begin{itemize}
\item  \ldots and you attack the same target, add its ferocity to your damage
\item  \ldots and you track, add its cunning to your roll
\item  \ldots and you take damage, add its armor to your armor
\item  \ldots and you discern realities, add its cunning to your roll
\item  \ldots and you parley, add its cunning to your roll
\item  \ldots and someone interferes with you, add its instinct to their roll

\end{itemize}
\section*{Alignment}


{\bfseries Choose an alignment:}
\subsection{Chaotic}


 Free someone from literal or figurative bonds.
\subsection{Good}


 Endanger yourself to combat an unnatural threat.
\subsection{Neutral}


 Help an animal or spirit of the wild.
\section*{Gear}


 Your load is 11+Str. You start with dungeon rations (5 uses, 1 weight), leather armor (1 armor, 1 weight), and a bundle of arrows (3 ammo, 1 weight). Choose your armament:
\begin{itemize}
\item Hunter's bow (near, far, 1 weight) and short sword (close, 1 weight)
\item Hunter's bow (near, far, 1 weight) and spear (reach, 1 weight)

\end{itemize}


 Choose one:
\begin{itemize}
\item Adventuring gear (1 weight) and dungeon rations (1 weight)
\item Adventuring gear (1 weight) and bundle of arrows (3 ammo, 1 weight)

\end{itemize}
\section*{Bonds}


 Fill in the name of one of your companions in at least one:


 I have guided \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ before and they owe me for it.


 \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ is a friend of nature, so I will be their friend as well.


 \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ has no respect for nature, so I have no respect for them.


 \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ does not understand life in the wild, so I will teach them.
\section*{Advanced Moves}


 You may take this move only if it is your first advancement.
\subsection{Half-Elven}


 Somewhere in your lineage lies mixed blood and it begins to show its presence. You gain the elf starting move if you took the human one at character creation or vice versa.


\vspace{\baselineskip}
 {\bfseries When you gain a level from 2-5, choose from these moves.}
\subsection{Wild Empathy}


 You can speak with and understand animals.
\subsection{Familiar Prey}


 When you spout lore about a monster you use WIS instead of INT.
\subsection{Viper's Strike}


 When you strike an enemy with two weapons at once, add an extra 1d4 damage for your off-hand strike.
\subsection{Camouflage}


 When you \textbf{keep still in natural surroundings}
, enemies never spot you until you make a movement.
\subsection{Man's Best Friend}


 When you \textbf{allow your animal companion to take a blow that was meant for you}
, the damage is negated and your animal companion's ferocity becomes 0. If its ferocity is already 0 you can't use this ability. When you have a few hours of rest with your animal companion its ferocity returns to normal.
\subsection{Blot Out the Sun}


 When you volley you may spend extra ammo before rolling. For each point of ammo spent you may choose an extra target. Roll once and apply damage to all targets.
\subsection{Well-Trained}


 Choose another training for your animal companion.
\subsection{God Amidst the Wastes}


 Dedicate yourself to a deity (name a new one or choose one that's already been established). You gain the commune and cast a spell cleric moves. When you select this move, treat yourself as a cleric of level 1 for using spells. Every time you gain a level thereafter, increase your effective cleric level by 1.
\subsection{Follow Me}


 When you undertake a perilous journey you can take two roles. You make a separate roll for each.
\subsection{A Safe Place}


 When you \textbf{set the watch for the night}
, everyone takes +1 to take watch.


\vspace{\baselineskip}
 {\bfseries When you gain a level from 6-10, choose from these moves or the level 2-5 moves.}
\subsection{Wild Speech}


 Replaces: Wild Empathy


 You can speak with and understand any non-magical, non-planar creature.
\subsection{Hunter's Prey}


 Replaces: Familiar Prey


 When you spout lore about a monster you use WIS instead of INT\@. On a 12+, in addition to the normal effects, you get to ask the GM any one question about the subject.
\subsection{Viper's Fangs}


 Replaces: Viper's Strike


 When you strike an enemy with two weapons at once, add an extra 1d8 damage for your off-hand strike.
\subsection{Smaug's Belly}


 When you know your target's weakest point your arrows have 2 piercing.
\subsection{Strider}


 Replaces: Follow Me


 When you undertake a perilous journey you can take two roles. Roll twice and use the better result for both roles.
\subsection{A Safer Place}


 Replaces: A Safe Place


 When you set the watch for the night everyone takes +1 to take watch. After a night in camp when you set the watch everyone takes +1 forward.
\subsection{Observant}


 When you hunt and track, on a hit you may also ask one question about the creature you are tracking from the discern realities list for free.
\subsection{Special Trick}


 Choose a move from another class. So long as you are working with your animal companion you have access to that move.
\subsection{Unnatural Ally}


 Your animal companion is a monster, not an animal. Describe it. Give it +2 ferocity and +1 instinct, plus a new training.


